---
title: "CryptoAnalysisResults"
author: "Rodrigo Bonifácio et al."
date: "12/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sqldf)
setwd(".")
```

## Crypto Analysis

To understand which JCA APIs report more warnings using the CognicCrypt approach, 
we explored two datasets:

   * AndroidCryptoMine from Luis Amaral et al. (unpublished)

   * CryptoMine from Mohammadreza Hazhirpasand, Mohammad Ghafari, and Oscar Nierstrasz. 2020. *Java Cryptography Uses in the Wild*. In Proceedings of the 14th ACM / IEEE International Symposium on Empirical Software Engineering and Measurement (ESEM) (ESEM '20). 
   


```{r load}
# CryptoMine
cm <- read.csv("CryptoMine.csv", sep=",")
cm <- sqldf("select Project_url as project, API_name as rule, Misuse_type as misuse 
             from cm")

# AndroidCryptoMine
acm <- read.csv("AndroidCryptoMine.csv", sep=",")
acm <- sqldf("select Project as project, ViolatedRule as rule, ErrorType as misuse 
             from acm")
```

### Summary of Violations for CryptoMine

```{r summary-cm}
# total of violations: 

sqldf("select count(*) from cm")

# total of violations (over rule)

sqldf("select rule, count(*) from cm 
       group by rule 
       order by 2 desc")
```


### Summary of Violations for AndroidCryptoMine

```{r summary-acm}
# total of violations: 

sqldf("select count(*) from acm")

# total of violations (over rule)

sqldf("select rule, count(*) from acm 
       group by rule 
       order by 2 desc")
```
